EDIpack2: interoperable Lanczos-based solver for generic quantum impurity problems

### 2025-05-14 04_cbinding.tex
Minimal tweak

\begin{lstlisting}
push!(LOAD_PATH, joinpath(@__DIR__, "PATH_TO_REPO/EDIjl2/src"))
\end{lstlisting}

@@

\begin{lstlisting}
using EDIjl2
\end{lstlisting}

@@

\begin{lstlisting}
EDIjl2.read_input("inputED.conf")
ed = EDIjl2.global_env
println("Nspin = ", ed.Nspin)
ed.Nspin = 2
\end{lstlisting}

>>>>

\begin{lstlisting}[style=mybash]
push!(LOAD_PATH, joinpath(@__DIR__, "PATH/TO/REPO/src"))
\end{lstlisting}

@@

\begin{lstlisting}[style=mybash]
using EDIjl2
\end{lstlisting}

@@

\begin{lstlisting}[style=mybash]
EDIjl2.read_input("inputED.conf")
ed = EDIjl2.global_env
println("Nspin = ", ed.Nspin)
ed.Nspin = 2
\end{lstlisting}

### 2025-05-14 05_examples.tex
Minimal tweak

\subsection{Multi-orbital impurity with Hubbard-Kanamori interaction (TRIQS)}
\label{SecExamplesTRIQS}

The third example demonstrates how to use the edipack2triqs compatibility
layer (Sec.~\ref{sSecInteropTRIQS}) to solve a quantum system comprised by a
3-orbital correlated impurity coupled to a few non-interacting bath sites.
The interaction term of the impurity Hamiltonian has the Hubbard-Kanamori
form (\ref{Hint}).

A Python script implementing a calculation that makes use of edipack2triqs
generally begins with a few module imports.
\lstinputlisting[style=mypython,
                 numbers=none,
                 basicstyle={\scriptsize\ttfamily},
                 firstline=1, lastline=13]
{edipack2_examples/edipack2triqs/hubbard_kanamori.py}

One then proceeds to defining the system under consideration. In this case we
consider an impurity atom with three correlated orbitals and two bath states
per each impurity orbital. This information must be encoded in the fundamental
set objects that are later used to construct the solver.
\lstinputlisting[style=mypython,
                 numbers=none,
                 basicstyle={\scriptsize\ttfamily},
                 firstline=15, lastline=26]
{edipack2_examples/edipack2triqs/hubbard_kanamori.py}
The next step is to define a TRIQS many-body operator expression that represents
the Hamiltonian to be diagonalized.
\lstinputlisting[style=mypython,
                 numbers=none,
                 basicstyle={\scriptsize\ttfamily},
                 firstline=28, lastline=67]
{edipack2_examples/edipack2triqs/hubbard_kanamori.py}
Finally, one creates a solver object and performs the actual calculation by
calling its method {\tt solve()}. This is normally the most time- and
memory-consuming step.
\lstinputlisting[style=mypython,
                 numbers=none,
                 basicstyle={\scriptsize\ttfamily},
                 firstline=69, lastline=83]
{edipack2_examples/edipack2triqs/hubbard_kanamori.py}
The computation results are readily available as attributes of the solver
object. The following code snippet shows how to access measured expectation
values of the static observables, and how to employ the plotting framework of
TRIQS to visualize the obtained Matsubara and real-frequency impurity Green's
functions (Fig.~\ref{figEx3}).
\lstinputlisting[style=mypython,
                 mathescape=false,
                 numbers=none,
                 basicstyle={\scriptsize\ttfamily},
                 firstline=85, lastline=112]
{edipack2_examples/edipack2triqs/hubbard_kanamori.py}

\begin{figure}[t!]
    \includegraphics[width=0.5\linewidth]
        {edipack2_examples/edipack2triqs/G_iw.pdf}
    \includegraphics[width=0.5\linewidth]
        {edipack2_examples/edipack2triqs/A_w.pdf}
    \caption{\label{figEx3}%
        Imaginary part of the Matsubara Green's function (left) and the
        corresponding orbital-resolved spectral function (right) computed for a
        three-orbital impurity model with an interaction of the Hubbard-Kanamori
        type (\ref{Hint}). This illustration is produced by the edipack2triqs
        example script presented in Sec.~\ref{SecExamplesTRIQS}.
    }
\end{figure}

>>>>

\subsection{Multi-orbital Hubbard (TRIQS)}
